---
title: "Day5--Histograms, Scatter Plots, Outliers"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(palmerpenguins)
library(tidyverse)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda
- Finish Box Plots
- Histograms
- Scatter Plots
- Standard deviation

---

## Outlier in Chinstrap data

To begin with, filter out a data frame that only has the Chinstrap penguins in it:

```{r}
# look at the data
penguins_data <- penguins

# Filter Chinstrap
chinstrap <- filter(penguins, species == "Chinstrap")

```

Now plot a box plot for the body mass of Chinstrap penguins:

```{r}
# Body mass boxplot for Chinstrap penguins
ggplot(chinstrap, aes(y = body_mass_g)) + geom_boxplot()

```

Now compute the quantiles for the body mass of Chinstrap penguins

```{r}
# quantiles for body mass of Chinstrap penguins
quantile(chinstrap$body_mass_g)
```


Finally, compute the size of the whiskers by doing $Q_3 + 1.5 \times IQR$ and $Q_1 - 1.5 \times IQR$

```{r}
# compute the size of the whiskers
IQR <- 3950 - 3487.5
IQR(chinstrap$body_mass_g)
3950 + 1.5*IQR
3487.5 - 1.5*IQR
```

### Facets

```{r}
ggplot(penguins, aes(y=body_mass_g)) +
  geom_boxplot() + 
  facet_wrap(~species)

ggplot(penguins, aes(y=body_mass_g, color=species)) +
  geom_boxplot() 
```

## Histograms

```{r}
ggplot(penguins, aes(x = body_mass_g)) + geom_histogram(binwidth = 50)
```

## Scatterplots

## Standard Deviation

$$\text{standard deviation} = \sqrt{\text{variance}} = \sqrt{\sigma^2} = \sigma = \sqrt{\displaystyle \frac{\sum_{i=1}^n (\mu-x_i)^2}{N}}$$

## Standard deviation in a Sample

$$\text{standard deviation} = \sqrt{\text{variance}} = \sqrt{s^2} = s = \sqrt{\displaystyle \frac{\sum_{i=1}^n (\bar{x}-x_i)^2}{n-1}}$$

### Activities 

1. Find the a value of body mass for which $30 \%$ of penguins are below that mass.

```{r}

```

2. Find the a value of body mass for which $60 \%$ of penguins are above that mass.

```{r}

```


3. Make a box plot for flipper length.

```{r}

```


4. Make a boxplot for body mass where each island is separated into it's own boxplot.

```{r}

```


5. How many penguins are in the study are not from Torgesen?


6. How many penguins in the study have a flipper length less than $190$ and a body mass greater than $4700$?
